Principles for Open Data Curation: A Case Study with the New York City 311 Service Request Data

### 2024-06-13 manuscript/manuscript.tex
Updates

\usepackage[margin = 1in]{geometry}
\usepackage{amsmath}
\allowdisplaybreaks
\usepackage{authblk}
\usepackage{setspace}
\usepackage{natbib}
\usepackage{hyperref}\hypersetup{colorlinks=true, citecolor=blue}
\usepackage{parskip}
\usepackage{textgreek}
\usepackage{graphicx}
\usepackage{booktabs} % For better looking tables
\usepackage{siunitx} % For alignment of numbers
\usepackage{placeins}
\usepackage{caption}  % For custom captions
\usepackage{float}   % Required for the H specifier
\usepackage{adjustbox}

\usepackage[]{lineno}
\linenumbers*[1]
%% patches to make lineno work better with amsmath
\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
	\expandafter\let\csname old#1\expandafter\endcsname\csname
	#1\endcsname
	\expandafter\let\csname oldend#1\expandafter\endcsname\csname
	end#1\endcsname
	\renewenvironment{#1}%
	{\linenomath\csname old#1\endcsname}%
	{\csname oldend#1\endcsname\endlinenomath}}%
\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
	\patchAmsMathEnvironmentForLineno{#1}%
	\patchAmsMathEnvironmentForLineno{#1*}}%
\AtBeginDocument{%
	\patchBothAmsMathEnvironmentsForLineno{equation}%
	\patchBothAmsMathEnvironmentsForLineno{align}%
	\patchBothAmsMathEnvironmentsForLineno{flalign}%
	\patchBothAmsMathEnvironmentsForLineno{alignat}%
	\patchBothAmsMathEnvironmentsForLineno{gather}%
	\patchBothAmsMathEnvironmentsForLineno{multline}%
}

\sisetup{
  group-separator = {,},
  round-mode = places,
  round-precision = 0
}

@@

% \tableofcontents % Optional: Table of Contents
% \listoffigures % List of Figures
% \listoftables % List of Tables

@@

\noindent
{\it Keywords:}
Data science;
Open data;
Data cleansing;
Quality control;
Open Data Movement;
Data Democratization;
Transparency;
Data Curation;
Government Data;
NYC Open Data;
311 Service Request Data;
Data Validity;
Data Consistency;
Data Efficiency;
Smart Cities;
Public Engagement;
Research Data Management;

\end{abstract}

@@

The paper is organized as follows:
Section~\ref{sec:history} offers a brief review of the history of the 311 system. In 
Section~\ref{sec:trends} we take a look at long-term trends presented via a 10-year analysis.
Section~\ref{sec:issues} offers a general discussion of data cleansing issues
impacting data quality and curation efficiency. Section~\ref{sec:Structural} examines
the technical dimensions of the dataset, the structural issues. In Section~\ref{sec:datatypes} we examine the data fields
for compliance with the stated data type as found in the Data Dictionary. Section~\ref{sec:blanks} looks
at the data fields as regards missing, blank, or N/A entries. Section~\ref{sec:domain} explores
how data fields comply with a domain of legal or acceptable values. Section~\ref{sec:inconsistencies}
deals with the important issues surrounding logical inconsistencies and concerning patterns in the data. Section~\ref{sec:precision} 
explores the age-old issue of precision versus accuracy. Section~\ref{sec:duplicates}
identifies duplicate and redundant data fields. Section~\ref{sec:improvements} provides 
actionable suggestions for mitigating or resolving identified issues. Following this, Section~\ref{sec:protocol} outlines a series of general 
principles for the release of open data, drawing from our findings. The paper concludes with a discussion 
in Section~\ref{sec:discussion}, encapsulating the key insights and implications of our research.

@@

Today, the NYC 311 data system is a robust platform that manages a
vast array of urban living-related inquiries. The system handles over 3 million service 
requests (SRs) per year, encompassing such complaints as street noise, illegal parking, heat/hot water, abandoned vehicles,
and unsanitary conditions. The data, managed through a tailored application built on the 
Microsoft Dynamics and Azure platform, is a valuable resource for city
administration and policy-making. The 311 data is publicly accessible through the 
\href{https://opendata.cityofnewyork.us/}{NYC Open Data Portal} which provides access
to all the data sets (approx. 2700) and provides a convenient method for querying, grouping, aggregating, geo-mapping, visualization, and exporting
results. This open data initiative enables not only governmental transparency but also empowers 
researchers, civic developers, and the general public.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{Yearly.pdf}
  \caption{Yearly SR counts over 10-year period}
  \label{fig:yearly-counts}
\end{figure}

This 10-year timeframe (2014-2023) includes the COVID pandemic. Note that the pandemic
impact reached a peak in the July-September 2020 timeframe, accompanied by additional spikes
in the 2\textsuperscript{nd}half of 2021 as well. The all-time daily high for SRs occurred on Tuesday, 2020-08-04, 
with a spike of 24,415 SRs, a full 9.8 \textsigma's from the mean.

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{Monthly.pdf}
  \caption{Monthly SR counts over 10-year period}
  \label{fig:monthly-counts}
\end{figure}

A quick look at the corresponding  daily tend.  An average day is 8761 SRs.

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{Daily.pdf}
  \caption{Daily SR counts over 2022-2023 period}
  \label{fig:daily-counts}
\end{figure}

Seasonal trends are also prevalent. The months of November-thru-April are ``below average'' months, while the months May-thru-October are ``above average''. 
This seasonal trend is observed throughout the 10-year period as visualized here.

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{Calendar-Month.pdf}
  \caption{Calendar Month SR counts over a 10-year period}
  \label{fig:calendar-months-counts}
\end{figure}

@@

\begin{table}[H]
    \centering
    \small
    \begin{tabular}{@{}lll|lll@{}}
        \toprule
        \multicolumn{3}{c|}{Top 5 Days} & \multicolumn{3}{c}{Bottom 5 Days} \\
        \cmidrule(r){1-3} \cmidrule(l){4-6}
        Date & Count & Rank & Date & Count & Rank \\
        \midrule
        2020-08-04 & 24,415 & 1 & 2014-12-25 & 2965 & 1 \\
        2020-08-05 & 19,560 & 2 & 2015-12-25 & 3247 & 2 \\
        2023-09-29 & 17,962 & 3 & 2014-04-20 & 3287 & 3 \\
        2020-07-05 & 16,916 & 4 & 2015-12-26 & 3405 & 4 \\
        2020-06-21 & 15,883 & 5 & 2016-11-06 & 3419 & 5 \\
        \bottomrule
    \end{tabular}
    \caption{Top 5 and Bottom 5 Days}
    \label{tab:combined_counts}
\end{table}

\FloatBarrier % Ensure all floats before this point are processed before moving on

@@

\begin{figure}[H]
  \centering
	  \includegraphics[width=\textwidth]{SRs_by_Agency.pdf}
	  \caption{SR counts by Agency and Cumulative Percentage}

\end{figure}

@@

\begin{figure}[H]
  \centering
	  \includegraphics[width=\textwidth]{SR_by_Complaint_Type.pdf}
	  \caption{Top 20 SR complaint\_type and Cumulative Percentage}
	  \label{fig:SR_complaints}
\end{figure}

@@

\begin{table}[H]
    \centering
    \footnotesize
    \begin{tabular}{lS[table-format=7]S[table-format=2.2]l} % 'l' for left-aligned, 'S' for siunitx number alignment
        \toprule
        \textbf{complaint\_type} & \textbf{Count} & \textbf{Percentage} & \textbf{Agency} \\ 
        \midrule
        NOISE - RESIDENTIAL        & 675,502 & 10.56 & NYPD  \\ 
        NOISE - STREET/SIDEWALK    & 300,507 &  4.70 & NYPD  \\ 
        NOISE - COMMERCIAL         & 128,892 &  2.02 & NYPD  \\ 
        NOISE - VEHICLE            & 115,956 &  1.81 & NYPD  \\ 
        NOISE                      & 100,413 &  1.57 & DEP   \\ 
        NOISE - HELICOPTER         &  85,345 &  1.33 & EDC   \\ 
        NOISE - PARK               &  16,620 &  0.26 & NYPD  \\ 
        NOISE - HOUSE OF WORSHIP   &   2757 &  0.04 & NYPD  \\ 
        \bottomrule
    \end{tabular}
    \caption{Noise-related complaints\_type(s) by count with Agency}
    \label{tab:noisecomplaints}
\end{table}

@@

\begin{figure}[H]
  \centering
	  \includegraphics[width = \textwidth] {computed_columns_screenshot.png}
	  \caption{Screenshot of data portal showing the ``@computed'' columns}
	  \label{fig:computed-columns}
\end{figure}

@@

\begin{table}[ht]
\centering
\resizebox{0.8\linewidth}{!}{%
\scriptsize
\begin{tabular}{lrrrl}
	\toprule
	\textbf{Field} & \textbf{Total Empty} & \textbf{Percent Empty} & \textbf{N/A Count} \\
	\midrule
		taxi\_company\_borough & 6391341 & 99.94 & 0 \\
		road\_ramp & 6379080 & 99.75 & 0 \\
		vehicle\_type & 6376266 & 99.71 & 0 \\
		due\_date & 6370497 & 99.62 & 6370497 \\
		bridge\_highway\_direction & 6367626 & 99.57 & 0 \\
		bridge\_highway\_name & 6340197 & 99.14 & 0 \\
		bridge\_highway\_segment & 6340190 & 99.14 & 0 \\
		taxi\_pick\_up\_location & 6329954 & 98.98 & 0 \\
		facility\_type & 5966588 & 93.30 & 0 \\
		landmark & 2635736 & 41.22 & 0 \\
		intersection\_street\_1 & 2143847 & 33.52 & 0 \\
		intersection\_street\_2 & 2140707 & 33.48 & 0 \\
		cross\_street\_1 & 1846594 & 28.88 & 0 \\
		cross\_street\_2 & 1846008 & 28.87 & 0 \\
		location\_type & 798775 & 12.49 & 0 \\
		bbl & 768109 & 12.01 & 0 \\
		city & 332086 & 5.19 & 0 \\
		street\_name & 280463 & 4.39 & 0 \\
		incident\_address & 280268 & 4.38 & 0 \\
		closed\_date & 248839 & 3.89 & 248839 \\
		resolution\_description & 132333 & 2.07 & 0 \\
		zip\_codes & 123167 & 1.93 & 0 \\
		borough\_boundaries & 101453 & 1.59 & 0 \\
		community\_districts & 101445 & 1.59 & 0 \\
		city\_council\_districts & 101445 & 1.59 & 0 \\
		police\_precincts & 101445 & 1.59 & 0 \\
		police\_precinct & 101416 & 1.59 & 0 \\
		latitude & 99778 & 1.56 & 0 \\
		longitude & 99778 & 1.56 & 0 \\
		location & 99778 & 1.56 & 0 \\
		x\_coordinate\_state\_plane & 99668 & 1.56 & 0 \\
		y\_coordinate\_state\_plane & 98822 & 1.55 & 0 \\
		resolution\_action\_updated\_date & 91399 & 1.43 & 91399 \\
		incident\_zip & 83220 & 1.30 & 2 \\
		descriptor & 74645 & 1.17 & 0 \\
		address\_type & 38655 & 0.60 & 0 \\
		unique\_key & 0 & 0.00 & 0 \\
		agency & 0 & 0.00 & 0 \\
		agency\_name & 0 & 0.00 & 0 \\
		complaint\_type & 0 & 0.00 & 0 \\
		status & 0 & 0.00 & 0 \\
		community\_board & 0 & 0.00 & 0 \\
		borough & 0 & 0.00 & 0 \\
		open\_data\_channel\_type & 0 & 0.00 & 0 \\
		park\_facility\_name & 0 & 0.00 & 0 \\
		park\_borough & 0 & 0.00 & 0 \\
		created\_date & 0 & 0.00 & 0 \\
	\bottomrule
\end{tabular}
}
\caption{Blank and N/A entries by Field}
\end{table}

\FloatBarrier % Ensure all floats before this point are processed before moving on

@@

\begin{figure}[H]
  \centering
	  \includegraphics[width=\textwidth]{BlankFields.pdf}
	  \caption{Number and Percentage of Empty Entries}
	  \label{fig:blank_fields}
\end{figure}

@@

	\subsection{Issues with Zip Codes}
	\label{sec:zip-codes}
	 Unfortunately some fields proved to be  problematic when comparing the values to a domain of legal values.
	 For example, all zip codes (two fields: zip\_codes and incident\_zip) should be valid as defined by the USPS database
	 which contains 37,946 valid zip codes.

@@

	\begin{figure}[H]
	  \centering
		  \includegraphics[width=\textwidth]{invalid_incident_zip.pdf}
		  \caption{Invalid incident-zip by Agency}
		  \label{fig:invalid_incident_zip}
	\end{figure}

@@

	\begin{figure}[H]
	    		\centering
	    		\includegraphics[scale = 0.6]{zipcode_casestudy.png}
	    		\caption{Top 10 zip codes for Noise complaints (Zip Codes)}
	    	\label{fig:casestudy1-zipcodes}
		\end{figure}

@@

		\begin{figure}[H]
	    		\centering
	    		\includegraphics[scale = 0.6]{incident_zip_casestudy.png}
	    		\caption{Top 10 zip codes for Noise complaints(Incident Zip)}
	    	\label{fig:casestudy1-incident-zip}
		\end{figure}

@@

	\begin{table}[H]
	\centering
	\footnotesize
	\begin{tabular}{lrr@{\hskip 0.5cm}|@{\hskip 0.5cm}lrr}
	\toprule
	\multicolumn{3}{c}{\textbf{zip\_codes}} & \multicolumn{3}{c}{\textbf{incident\_zip}} \\
	\cmidrule(r){1-3} \cmidrule(l){4-6}
	\textbf{Zip Code} & \textbf{Count} & \textbf{Valid?} & \textbf{Zip Code} & \textbf{Count} & \textbf{Valid?} \\
		\midrule
		11275 & 104,556 & FALSE & 10466 & 104,562 & TRUE \\
		12420 & 27,503 & TRUE & 10023 & 27,972 & TRUE \\
		12428 & 26,564 & TRUE & 10031 & 25,548 & TRUE \\
		10935 & 25,508 & FALSE & 10457 & 25,066 & TRUE \\
		10934 & 23,448 & FALSE & 10453 & 24,752 & TRUE \\
		10931 & 22,381 & TRUE & 10456 & 24,751 & TRUE \\
		10930 & 22,121 & TRUE & 10452 & 22,527 & TRUE \\
		17613 & 21,963 & FALSE & 10025 & 21,705 & TRUE \\
		10936 & 21,707 & FALSE & 10458 & 21,689 & TRUE \\
		11606 & 21,435 & FALSE & 10032 & 20,622 & TRUE \\
		\bottomrule
	\end{tabular}
	\caption{Comparison of Top Ten Zip Codes Lists}
	\end{table}

@@

	\begin{table}[ht]
	\footnotesize
	\centering
		\begin{tabular}{ccccc}
		\toprule
		\textbf{Invalid Precinct} & \textbf{police\_precinct count} & \textbf{police\_precincts count} & \textbf{Delta}\\
		\midrule
			62 & 151808 & 151720 & 88 \\
			72 & 148881 & 148796 & 85 \\
			67 & 133171 & 133115 & 56 \\
			64 & 111236 & 111221 & 15 \\
			60 & 105252 & 105317 & -65 \\
			65 & 103334 & 103306 & 28 \\
			53 & 100097 & 100074 & 23 \\
			73 & 97746 & 97755 & -9 \\
			68 & 94204 & 94254 & -50 \\
			66 & 93654 & 93848 & -194 \\
		\bottomrule
		\end{tabular}
	\caption{Comparison of the fields police\_precinct and police\_precincts}
	\label{tab:comparison-precincts-diff}
	\end{table}

@@

	\begin{figure}[H]
	  \centering
		  \includegraphics[width=\textwidth]{invalid_police_precincts.pdf}
		  \caption{Invalid NYPD precincts by Agency}
		  \label{fig:invalid_police_precincts_zip}
	\end{figure}

@@

		\begin{table}[H]
		\centering
		\footnotesize
		\begin{tabular}{rlr}
		\toprule
		\textbf{Rank} & \textbf{Invalid CB} & \textbf{Count} \\
			\midrule
				1 & 64 MANHATTAN & 7144 \\
				2 & 83 QUEENS & 5133 \\
				3 & 55 BROOKLYN & 3327 \\
				4 & 81 QUEENS & 3180 \\
				5 & 80 QUEENS & 2407 \\
				6 & 26 BRONX & 2364 \\
				7 & 28 BRONX & 1128 \\
				8 & 82 QUEENS & 1054 \\
				9 & 95 STATEN ISLAND & 515 \\
				10 & 27 BRONX & 514 \\
			\bottomrule
		\end{tabular}
		\caption{Top Ten Invalid 'community\_board' Values}
		\end{table}

@@

		\begin{figure}[H]
	 	 \centering
		  \includegraphics[width = \textwidth]{invalid_community_boards.pdf}
		  \caption{Invalid Community Board by Agency}
		  \label{fig:invalid_community_boards}
		\end{figure}

@@

\begin{table}[H]
    \centering
    \small
    \begin{tabular}{l l r l}
        \toprule
        \textbf{created\_date} & \textbf{closed\_date} & \textbf{duration} & \textbf{agency} \\
	        \midrule
	        2022-02-11 13:43:05 & 1900-01-01 & -44602 & DHS \\
	        2022-02-11 11:03:38 & 1900-01-01 & -44602 & DHS \\
	        2022-02-11 08:29:49 & 1900-01-01 & -44601 & DHS \\
	        2022-02-11 14:08:08 & 1900-01-01 & -44602 & DHS \\
	        2022-02-11 14:05:16 & 1900-01-01 & -44602 & DHS \\
	        \bottomrule
    \end{tabular}
    \caption{Sample of SRs with extremely large negative durations}
    \label{tab:extreme_negative_durations}
\end{table}

@@

\begin{figure}[H]
 	 \centering
	  \includegraphics[width = \textwidth]{negative_duration_SR_barchart.pdf}
	  \caption{SRs with a Negative Duration by Agency}
	  \label{fig:negative-duration}
\end{figure}

@@

\begin{figure}[H]
 	 \centering
	  \includegraphics[width = \textwidth]{negative_duration_SR_violin.pdf}
	  \caption{Negative duration distribution}
	  \label{fig:negative-duration-violin}
\end{figure}

>>>>

\usepackage[margin = 1in]{geometry}
\usepackage{amsmath}
\allowdisplaybreaks
\usepackage{authblk}
\usepackage{setspace}
\usepackage{natbib}
\usepackage{hyperref}\hypersetup{colorlinks=true, citecolor=blue}
\usepackage{parskip}
\usepackage{textgreek}
\usepackage{graphicx}
\usepackage{booktabs} % For better looking tables
\usepackage{siunitx} % For alignment of numbers
\usepackage{placeins}
\usepackage{caption}  % For custom captions
\usepackage{float}   % Required for the H specifier
\usepackage{adjustbox}
\usepackage[]{lineno}
\linenumbers*[1]

%% patches to make lineno work better with amsmath
\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
	\expandafter\let\csname old#1\expandafter\endcsname\csname
	#1\endcsname
	\expandafter\let\csname oldend#1\expandafter\endcsname\csname
	end#1\endcsname
	\renewenvironment{#1}%
	{\linenomath\csname old#1\endcsname}%
	{\csname oldend#1\endcsname\endlinenomath}}%
\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
	\patchAmsMathEnvironmentForLineno{#1}%
	\patchAmsMathEnvironmentForLineno{#1*}}%
\AtBeginDocument{%
	\patchBothAmsMathEnvironmentsForLineno{equation}%
	\patchBothAmsMathEnvironmentsForLineno{align}%
	\patchBothAmsMathEnvironmentsForLineno{flalign}%
	\patchBothAmsMathEnvironmentsForLineno{alignat}%
	\patchBothAmsMathEnvironmentsForLineno{gather}%
	\patchBothAmsMathEnvironmentsForLineno{multline}%
}

\sisetup{
    group-separator = {,},
    round-mode = places,
    round-precision = 2,
    output-decimal-marker = {.},
    table-number-alignment = center,
    table-figures-integer = 6,
    table-figures-decimal = 2,
    table-figures-uncertainty = 2
}

@@

\tableofcontents % Optional: Table of Contents
\listoffigures % List of Figures
\listoftables % List of Tables

@@

\noindent
\textit{Keywords:}
311 Service Request Data;
Data cleansing;
Data Consistency;
Data Curation;
Data Democratization;
Data Efficiency;
Data science;
Data Validity;
Government Data;
NYC Open Data;
Open Data Movement;
Open data;
Public Engagement;
Quality control;
Research Data Management;
Smart Cities;
Transparency;
\end{abstract}

@@

The paper is organized as follows:
Section~\ref{sec:history} offers a brief review of the history of the 311 system. In 
Section~\ref{sec:trends} we take a look at long-term trends presented via a 10-year analysis.
Section~\ref{sec:issues} offers a general discussion of data cleansing issues
impacting data quality and curation efficiency. Section~\ref{sec:structural} examines
the technical dimensions of the dataset, the structural issues. In Section~\ref{sec:datatypes} we examine the data fields
for compliance with the stated data type as found in the Data Dictionary. Section~\ref{sec:blanks} looks
at the data fields as regards missing, blank, or N/A entries. Section~\ref{sec:domain} explores
how data fields comply with a domain of legal or acceptable values. Section~\ref{sec:inconsistencies}
deals with the important issues surrounding logical inconsistencies and concerning patterns in the data. Section~\ref{sec:precision} 
explores the age-old issue of precision versus accuracy. Section~\ref{sec:duplicates}
identifies duplicate and redundant data fields. Section~\ref{sec:improvements} provides 
actionable suggestions for mitigating or resolving identified issues. Following this, Section~\ref{sec:protocol} outlines a series of general 
principles for the release of open data, drawing from our findings. The paper concludes with a discussion 
in Section~\ref{sec:discussion}, encapsulating the key insights and implications of our research.

@@

Today, the NYC 311 data system is a robust platform that manages a
vast array of urban living-related inquiries. The system handles over 3 million service 
requests (SRs) per year, encompassing such complaints as street noise, illegal parking, heat/hot water, abandoned vehicles,
and unsanitary conditions. The data, managed through a tailored application built on the 
Microsoft Dynamics and Azure platform, is a valuable resource for city
administration and policy-making. The 311 data is publicly accessible through the 
NYC Open Data Portal which provides access
to all the data sets (approx. 2700) and provides a convenient method for querying, grouping, aggregating, geo-mapping, visualization, and exporting
results. This open data initiative enables not only governmental transparency but also empowers 
researchers, civic developers, and the general public.

@@

\begin{figure}[tbp]
  \centering
  \caption{Yearly SR counts over 10-years}
  \includegraphics[width=\textwidth]{Yearly.pdf}
  \label{fig:yearly-counts}
\end{figure}

This 10-year timeframe (2014-2023) includes the COVID pandemic. INote that the pandemic
impact reached a peak in the July-September 2020 timeframe, accompanied by additional spikes
in the 2\textsuperscript{nd}half of 2021 as well. The all-time daily high for SRs occurred on Tuesday, 2020-08-04, 
with a spike of 24,415 SRs, a full 9.8 \textsigma's from the mean.

@@

\begin{figure}[htbp]
  \centering
   \caption{Monthly SR counts over 10-years}
  \includegraphics[width=\textwidth]{10-year-monthly.pdf}
  \label{fig:monthly-counts}
\end{figure}

@@

\begin{table}[tbp]
    \centering
    \small
    \caption{Top 5 and Bottom 5 Days for SRs}
    \begin{tabular}{@{}lll lll@{}}
        \toprule
        \multicolumn{3}{c}{Top 5 Days} & \multicolumn{3}{c}{Bottom 5 Days} \\
        \cmidrule(r){1-3} \cmidrule(l){4-6}
        Date & Count & Rank & Date & Count & Rank \\
        \midrule
        2020-08-04 & 24,415 & 1 & 2014-12-25 & 2965 & 1 \\
        2020-08-05 & 19,560 & 2 & 2015-12-25 & 3247 & 2 \\
        2023-09-29 & 17,962 & 3 & 2014-04-20 & 3287 & 3 \\
        2020-07-05 & 16,916 & 4 & 2015-12-26 & 3405 & 4 \\
        2020-06-21 & 15,883 & 5 & 2016-11-06 & 3419 & 5 \\
        \bottomrule
    \end{tabular}
    \label{tab:combined_counts}
\end{table}

%\FloatBarrier % Ensure all floats before this point are processed before moving on

@@

\begin{figure}[tbp]
	\centering
  	\caption{SR counts by Agency and Cumulative Percentage}
	\includegraphics[width=\textwidth]{SRs_by_Agency.pdf}  
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  	\caption{Top 20 SR complaint\_type and Cumulative Percentage}
	  \includegraphics[width=\textwidth]{SR_by_Complaint_Type.pdf}  
	  \label{fig:SR_complaints}
\end{figure}

@@

\begin{table}[tbp]
    \centering
    \caption{Noise-related complaints\_type(s) by count with Agency}
    \footnotesize
    \begin{tabular}{@{}lS[table-format=7.0,round-mode=places,round-precision=0]S[table-format=2.2,round-mode=places,round-precision=2]l@{}} % 'l' for left-aligned, 'S' for siunitx number alignment
        \toprule
        \textbf{complaint\_type} & \textbf{Count} & \textbf{Percentage} & \textbf{Agency} \\ 
        \midrule
        NOISE - RESIDENTIAL        & 675502 & 10.56 & NYPD  \\ 
        NOISE - STREET/SIDEWALK    & 300507 &  4.70 & NYPD  \\ 
        NOISE - COMMERCIAL         & 128892 &  2.02 & NYPD  \\ 
        NOISE - VEHICLE            & 115956 &  1.81 & NYPD  \\ 
        NOISE                      & 100413 &  1.57 & DEP   \\ 
        NOISE - HELICOPTER         &  85345 &  1.33 & EDC   \\ 
        NOISE - PARK               &  16620 &  0.26 & NYPD  \\ 
        NOISE - HOUSE OF WORSHIP   &   2757 &  0.04 & NYPD  \\ 
        \bottomrule
    \end{tabular}
    \label{tab:noisecomplaints}
\end{table}

@@

\begin{figure}[tbp]
  \centering
  \caption{Screenshot of data portal showing the ``@computed'' columns}
	  \includegraphics[width = 0.65\textwidth] {computed_columns_screenshot.pdf}	  
	  \label{fig:computed-columns}
\end{figure}

@@

\begin{table}[tbp]
\centering
\caption{Blank and N/A entries by Field}
\resizebox{0.8\linewidth}{!}{%
\scriptsize
\begin{tabular}{lrrrl}
	\toprule
	\textbf{Field} & \textbf{Total Empty} & \textbf{Percent Empty} & \textbf{N/A Count} \\
	\midrule
		taxi\_company\_borough & 6391341 & 99.94 & 0 \\
		road\_ramp & 6379080 & 99.75 & 0 \\
		vehicle\_type & 6376266 & 99.71 & 0 \\
		due\_date & 6370497 & 99.62 & 6370497 \\
		bridge\_highway\_direction & 6367626 & 99.57 & 0 \\
		bridge\_highway\_name & 6340197 & 99.14 & 0 \\
		bridge\_highway\_segment & 6340190 & 99.14 & 0 \\
		taxi\_pick\_up\_location & 6329954 & 98.98 & 0 \\
		facility\_type & 5966588 & 93.30 & 0 \\
		landmark & 2635736 & 41.22 & 0 \\
		intersection\_street\_1 & 2143847 & 33.52 & 0 \\
		intersection\_street\_2 & 2140707 & 33.48 & 0 \\
		cross\_street\_1 & 1846594 & 28.88 & 0 \\
		cross\_street\_2 & 1846008 & 28.87 & 0 \\
		location\_type & 798775 & 12.49 & 0 \\
		bbl & 768109 & 12.01 & 0 \\
		city & 332086 & 5.19 & 0 \\
		street\_name & 280463 & 4.39 & 0 \\
		incident\_address & 280268 & 4.38 & 0 \\
		closed\_date & 248839 & 3.89 & 248839 \\
		resolution\_description & 132333 & 2.07 & 0 \\
		zip\_codes & 123167 & 1.93 & 0 \\
		borough\_boundaries & 101453 & 1.59 & 0 \\
		community\_districts & 101445 & 1.59 & 0 \\
		city\_council\_districts & 101445 & 1.59 & 0 \\
		police\_precincts & 101445 & 1.59 & 0 \\
		police\_precinct & 101416 & 1.59 & 0 \\
		latitude & 99778 & 1.56 & 0 \\
		longitude & 99778 & 1.56 & 0 \\
		location & 99778 & 1.56 & 0 \\
		x\_coordinate\_state\_plane & 99668 & 1.56 & 0 \\
		y\_coordinate\_state\_plane & 98822 & 1.55 & 0 \\
		resolution\_action\_updated\_date & 91399 & 1.43 & 91399 \\
		incident\_zip & 83220 & 1.30 & 2 \\
		descriptor & 74645 & 1.17 & 0 \\
		address\_type & 38655 & 0.60 & 0 \\
		unique\_key & 0 & 0.00 & 0 \\
		agency & 0 & 0.00 & 0 \\
		agency\_name & 0 & 0.00 & 0 \\
		complaint\_type & 0 & 0.00 & 0 \\
		status & 0 & 0.00 & 0 \\
		community\_board & 0 & 0.00 & 0 \\
		borough & 0 & 0.00 & 0 \\
		open\_data\_channel\_type & 0 & 0.00 & 0 \\
		park\_facility\_name & 0 & 0.00 & 0 \\
		park\_borough & 0 & 0.00 & 0 \\
		created\_date & 0 & 0.00 & 0 \\
	\bottomrule
\end{tabular}
}
\end{table}

%\FloatBarrier % Ensure all floats before this point are processed before moving on

@@

\begin{figure}[tbp]
  \centering
  	\caption{Number and Percentage of Empty Entries}
	\includegraphics[width=\textwidth]{BlankFields.pdf}
	\label{fig:blank_fields}
\end{figure}

@@

	\subsection{Issues with Zip Codes}
	\label{sec:zipcodesissues}
	 Unfortunately some fields proved to be  problematic when comparing the values to a domain of legal values.
	 For example, all zip codes (two fields: zip\_codes and incident\_zip) should be valid as defined by the USPS database
	 which contains 37,946 valid zip codes.

@@

	\begin{figure}[tbp]
	  \centering
	  	\caption{Invalid incident-zip by Agency}
		\includegraphics[width=\textwidth]{invalid_incident_zip.pdf} 
		\label{fig:invalid_incident_zip}
	\end{figure}

@@

@@

@@

\begin{table}[tbp]
    \centering
    \footnotesize
    \caption{Comparison of Top Ten Zip Codes Lists}
    \begin{tabular}{@{}lS[table-format=6.0,round-mode=places,round-precision=0]c@{\hskip 0.5cm}@{}lS[table-format=6.0,round-mode=places,round-precision=0]c@{}}
        \toprule
        \multicolumn{3}{c}{\textbf{zip\_codes}} & \multicolumn{3}{c}{\textbf{incident\_zip}} \\
        \cmidrule(r){1-3} \cmidrule(l){4-6}
        \textbf{Zip Code} & \textbf{Count} & \textbf{Valid?} & \textbf{Zip Code} & \textbf{Count} & \textbf{Valid?} \\
        \midrule
        11275 & 104556 & FALSE & 10466 & 104562 & TRUE \\
        12420 & 27503 & TRUE & 10023 & 27972 & TRUE \\
        12428 & 26564 & TRUE & 10031 & 25548 & TRUE \\
        10935 & 25508 & FALSE & 10457 & 25066 & TRUE \\
        10934 & 23448 & FALSE & 10453 & 24752 & TRUE \\
        10931 & 22381 & TRUE & 10456 & 24751 & TRUE \\
        10930 & 22121 & TRUE & 10452 & 22527 & TRUE \\
        17613 & 21963 & FALSE & 10025 & 21705 & TRUE \\
        10936 & 21707 & FALSE & 10458 & 21689 & TRUE \\
        11606 & 21435 & FALSE & 10032 & 20622 & TRUE \\
        \bottomrule
    \end{tabular}
    \label{tab:zipcodes}
\end{table}

@@

	\begin{table}[tbp]
	\footnotesize
	\centering
	\caption{Comparison of the fields police\_precinct and police\_precincts}
		\begin{tabular}{ccccc}
		\toprule
		\textbf{Invalid Precinct} & \textbf{police\_precinct count} & \textbf{police\_precincts count} & \textbf{Delta}\\
		\midrule
			62 & 151808 & 151720 & 88 \\
			72 & 148881 & 148796 & 85 \\
			67 & 133171 & 133115 & 56 \\
			64 & 111236 & 111221 & 15 \\
			60 & 105252 & 105317 & -65 \\
			65 & 103334 & 103306 & 28 \\
			53 & 100097 & 100074 & 23 \\
			73 & 97746 & 97755 & -9 \\
			68 & 94204 & 94254 & -50 \\
			66 & 93654 & 93848 & -194 \\
	\bottomrule
	\end{tabular}
	\label{tab:comparison-precincts-diff}
	\end{table}

@@

	\begin{figure}[tbp]
	  \centering
	  \caption{Invalid NYPD precincts by Agency}
		  \includegraphics[width=\textwidth]{invalid_police_precincts.pdf}	  
		  \label{fig:invalid_police_precincts_zip}
	\end{figure}

@@

		\begin{table}[tbp]
		\centering
		\caption{Top Ten Invalid 'community\_board' Values}
		\footnotesize
		\begin{tabular}{rlr}
		\toprule
		\textbf{Rank} & \textbf{Invalid CB} & \textbf{Count} \\
			\midrule
				1 & 64 MANHATTAN & 7144 \\
				2 & 83 QUEENS & 5133 \\
				3 & 55 BROOKLYN & 3327 \\
				4 & 81 QUEENS & 3180 \\
				5 & 80 QUEENS & 2407 \\
				6 & 26 BRONX & 2364 \\
				7 & 28 BRONX & 1128 \\
				8 & 82 QUEENS & 1054 \\
				9 & 95 STATEN ISLAND & 515 \\
				10 & 27 BRONX & 514 \\
			\bottomrule
		\end{tabular}
		\end{table}

@@

		\begin{figure}[tbp]
	 	 \centering
		  \includegraphics[width = \textwidth]{invalid_community_boards.pdf}
		  \caption{Invalid Community Board by Agency}
		  \label{fig:invalid_community_boards}
		\end{figure}

@@

\begin{table}[tbp]
    \centering
    \caption{Sample of SRs with extremely large negative durations}
    \small
    \begin{tabular}{l l r l}
        \toprule
        \textbf{created\_date} & \textbf{closed\_date} & \textbf{duration} & \textbf{agency} \\
	        \midrule
	        2022-02-11 13:43:05 & 1900-01-01 & -44602 & DHS \\
	        2022-02-11 11:03:38 & 1900-01-01 & -44602 & DHS \\
	        2022-02-11 08:29:49 & 1900-01-01 & -44601 & DHS \\
	        2022-02-11 14:08:08 & 1900-01-01 & -44602 & DHS \\
	        2022-02-11 14:05:16 & 1900-01-01 & -44602 & DHS \\
	        \bottomrule
    \end{tabular}
    \label{tab:extreme_negative_durations}
\end{table}

@@

\begin{figure}[tbp]
 	 \centering
 	 \caption{SRs with a Negative Duration by Agency}
	  \includegraphics[width = \textwidth]{negative_duration_SR_barchart.pdf}
	  \label{fig:negative-duration}
\end{figure}

@@

\begin{figure}[tbp]
 	 \centering
 	 \caption{Negative duration distribution}
	  \includegraphics[width = \textwidth]{negative_duration_SR_violin.pdf}
	  \label{fig:negative-duration-violin}
\end{figure}
